---
Title: "Homework1"
Author: "Harsha Senapathi, svs2130"
Date: "9/20/2019"
Output: github_document
---

## Loading required Library
```{r Library}

# Loading Library
library(tidyverse)

```


# Problem 1

## Creating a data frame and calculating the means of all the variables

```{r Problem_1, warning=FALSE}

# Problem 1
# Creating a data frame

set.seed(10)
problem1_df= tibble(
  random = rnorm(8),
  vec_logical = random > 0,
  vec_char = c("a", "b", "c", "d", "e", "f", "g", "h"),
  vec_factor = as.factor(c(1,2,3,1,1,2,3,2))
)

# Since the argument is numeric, we get a value.
# Works, we get a value.
mean(pull(problem1_df, random)) 


# Since the argument is logical, we get a value.
# Works, We get a value.
mean(problem1_df$vec_logical)


# Since the argument isn't numeric or logical, the result is NA.
# Doesnt work, we get NA.
mean(problem1_df$vec_char)


# Since the argument is neither numberic nor logical, the result is NA
# Doesnt work, we get NA
mean(problem1_df$vec_factor) 


# Coercing the character variables as numeric.
# It doesn't work because cannot take mean of characters.
mean(as.numeric(problem1_df$vec_char))


# Coercing factor vector as numeric.
# It works we get a value.
mean(as.numeric(problem1_df$vec_factor))

     
```

## Using variables from the dataframe **problem1_df** Multiplying different variables

```{r Problem_1second, warning=FALSE}

# second code chunk

# Coercing logical vector as numeric and multiplying with Random variable
as.numeric(problem1_df$vec_logical)*(problem1_df$random)

# Coercing logical vector as factor and multiplying with Random variable
as.factor(problem1_df$vec_logical)*(problem1_df$random)

# Coercing factor of logical vector as numeric and multiplyng with random
as.numeric(as.factor(problem1_df$vec_logical))*(problem1_df$random)
```


# Problem #2

## Creating ggplots

### Creating a new dataframe

```{r Problem2, warning=FALSE}

# Creating dataframe
set.seed(1)
problem2_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  vec_logical = c(x + y > 1),
  vec_numeric = c(vec_logical),
  vec_factor = c(vec_logical)
)
```


### A short description of our dataframe

* The number of rows in our data set is **`r nrow(problem2_df)`**.
* The number of columns in our dataset is **`r ncol(problem2_df)`**.
* The mean, median and Standard deviation of *x* are **`r mean(problem2_df$x)`, `r median(problem2_df$x)` and `r sd(problem2_df$x)`** respectively
* The proportion of cases for which the logical vector(x + y > 1) is true: **`r length(problem2_df$vec_logical[which(problem2_df$vec_logical == 'TRUE')]) / nrow(problem2_df)`**.


### Using the above dataframe **problem2_df** to create Scatter Plots

```{r scatter_plot, warning=FALSE}

# Creating a scatter plot of the logical vector
ggplot(problem2_df, aes(x = x, y = y, color = vec_logical)) + geom_point()

# Saving the ggplot as a png file
ggsave(filename = "C:/Users/shvar/OneDrive - cumc.columbia.edu/Data Science/P8105_HW/problem2_df_color_logical_ggplot.png")

# Creating a scatter plot using the numeric vector
ggplot(problem2_df, aes(x = x, y = y, color = vec_numeric)) + geom_point()


# Creating a scatter plot using the factor vector
ggplot(problem2_df, aes(x = x, y = y, color = vec_factor)) + geom_point()

```


